### 2017-07-28 Manuscript/SW_early_life_telomeres_FULL.Rmd
Edits for publication

---
output:
  pdf_document:
bibliography: MyBib.bib
header-includes: \usepackage{graphicx}
    \usepackage{setspace}
    \doublespacing
    \usepackage{lineno}
    \linenumbers
---
```{r setup, include = F}

@@

##Data accessibility
This manuscript was written in R Markdown (http://rmarkdown.rstudio.com/). All data and scripts required to reproduce the manuscript, figures and analyses will be made available on GitHub.

@@

**Figure 1**

```{r Figure 1}

@@

@@

@@

**Figure 2**

```{r Figure 2}

@@

multiplot(Fig2A,Fig2B,Fig2C,Fig2D,layout = matrix(c(1,2,3,4),nrow = 2,byrow = T))

@@

**Figure 3**

```{r Figure 3}

@@

multiplot(Fig3A,Fig3B,Fig3C,layout = matrix(c(1,1,2,3),byrow = T,nrow = 2))

>>>>

---
output:
  word_document:
bibliography: MyBib.bib
header-includes: \usepackage{graphicx}
    \usepackage{setspace}
    \doublespacing
    \usepackage{lineno}
    \linenumbers
---
```{r setup, include = F}

@@

##Data accessibility
This manuscript was written in R Markdown (http://rmarkdown.rstudio.com/). All data and scripts required to reproduce the manuscript, figures and analyses are available on GitHub (doi: 10.5281/zenodo.835844).

@@

```{r Figure 1,include = F}

@@

pdf("Figures/Figure 1.pdf",
    width = 10,
    height = 8,
    paper = "a4")

@@

dev.off()
```

@@

```{r Figure 2,include = F}

@@

pdf("Figures/Figure 2.pdf",
    width = 10,
    height = 8,
    paper = "a4")
multiplot(Fig2A,Fig2B,Fig2C,Fig2D,layout = matrix(c(1,2,3,4),nrow = 2,byrow = T))
dev.off()

@@

```{r Figure 3,include = F}

@@

pdf("Figures/Figure 3.pdf",
    width = 10,
    height = 8,
    paper = "a4")
multiplot(Fig3A,Fig3B,Fig3C,layout = matrix(c(1,1,2,3),byrow = T,nrow = 2))
dev.off()

### 2017-07-28 Manuscript/SW_early_life_telomeres_SOM.Rmd
Home edits
Final edits before resub
Edits for publication

---
output: pdf_document
classoption: landscape
header-includes: \usepackage{graphicx}
---

@@

**Table S1** Cohort sizes for each birth year of the Seychelles warbler dataset used in this study.
```{r Table S1}
x <- subset(dd,!duplicated(BirdID)) %>%
  ddply(.(LayYear),
        summarise,
        N = length(RTL)) %>%
  `colnames<-`(c("Cohort", "N"))
kable(x)
```

@@

**Table S4** Model selection table for analysis of factors affecting $\Delta$RTL in Seychelles warblers, using longitudinal data. Only models that remained in the top model set for model averaging (AICc $\leq$ 6 compared to the top model) are included here. TQ = territory quality.

>>>>

---
output: word_document
classoption: landscape
header-includes: \usepackage{graphicx}
---

@@

**Table S1** Cohort sizes for each hatch year of the Seychelles warbler dataset used in this study. Note that cohort sizes on Cousin are typically small due to the saturated nature of the population.
```{r Table S1}
x <- subset(dd,!duplicated(BirdID)) %>%
  ddply(.(LayYear),
        summarise,
        N = length(RTL)) %>%
  `colnames<-`(c("Cohort", "N"))
kable(x)
```

@@

**Table S4** Model selection table for analysis of factors affecting $\Delta$RTL in Seychelles warblers, using longitudinal data. Only models that remained in the top model set for model averaging (AICc $\leq$ 6 compared to the top model) are included here.
